The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-04-03 paper.tex
UP TO SECTION 4

Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$).
\subsubsection{Observations}\label{subsubsec:Obs}

@@

The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
We observed 19-21 targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB). \\

@@

The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det}$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.

@@

The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we also discuss the approach followed to recover the morphological parameters for these galaxies.
We do not expect that this small number of galaxies without {\em HST} imaging will impact the bulk dynamical properties of the KDS sample.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}.}
\label{tab:phys-props}
\begin{tabular}{lllllllllll}

@@

ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & SFR$_{SED}$[$M_{\odot}yr^{-1}]$$^{b}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\

@@

b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 97 & 0.36        & 72        & 9     & 1.57      \\
b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76 & 172 & 0.28        & 78        & 146   & 0.52      \\
bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75  & 14 & 0.50         & 61        & 146   & 1.91      \\
bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1 & 10 & 0.44        & 66        & 168   & 1.83      \\
bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 20 & 0.50         & 61        & 67    & 1.59      \\
bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 33 & 0.80         & 37        & 148   & 1.24      \\
bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7 & 92 & 0.31        & 76        & 63    & 1.61      \\
bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9  & 6  & 0.65        & 50        & 49    & 0.87      \\
lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 5  & 0.64        & 52        & 1     & 1.28      \\
lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6  & 5  & 0.53        & 60        & 34    & 1.27      \\
lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 5  & 0.30         & 76        & 78    & 1.18      \\
lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 18  & 0.79         & 38        & 66    & 0.95      \\
lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9 & 64 & 0.60         & 54        & 40    & 1.88      \\
lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9 & 5  & 0.58        & 56        & 137   & 0.92      \\
lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 6  & 0.58        & 56        & 79    & 0.89 \\
lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9 & 8  & 0.22        & 84        & 81    & 1.16      \\
lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3  & 54 & 0.56        & 57        & 128   & 1.72      \\
lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7  & 8  & 0.60         & 54        & 119   & 1.98      \\
lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7  & 18 & 0.74        & 42        & 80    & 0.64      \\
lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6  & 6  & 0.79         & 38        & 43    & 0.46      \\
lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6  & 56 & 0.52        & 60        & 15    & 0.87      \\
lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 13  & 0.56         & 57        & 50    & 0.78      \\
$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5 & 14 & 0.57         & 57        & -    & 2.52      \\
n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7  & 3            & 0.75        & 42        & 84    & 1.06      \\
n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8  & 4            & 0.71        & 46        & 94    & 0.56      \\
lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2  & 4            & 0.85        & 32        & 27    & 0.46      \\
$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4  & 7            & 0.57         & 57        & -    & 2.18      \\
s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7  & 60            & 0.39        & 70        & 125   & 1.78      \\
s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5  & 45            & 0.57        & 57        & 76    & 1.59      \\
$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2 & 9            & 0.57         & 57        & -    & 3.30      \\
s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1 & 5            & 0.65        & 50        & 60   & 0.5       \\
$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6  & 10            & 0.57         & 57        & -    & 1.39

\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
      \item $^{b}$ Representative error of 0.4 dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ unconstrained; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
For the galaxies without {\em HST} coverage the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
This corresponds to a factor $\simeq1.3$ contribution to the uncertainty in the derived velocities for these galaxies.

@@

If a spaxel did not meet the criteria we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
This was carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
The criteria were then re-examined, and if satisfied, the Monte-Carlo procedure was carried out. 
If the binned spaxels fail the criteria, one final iteration was carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk.
If after the widest binning the criteria weren't satisfied, no value was assigned to that spaxel in the extracted maps. \\

The process was automated and applied to each of the 62 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
Following the fitting procedure the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
We find that 47 (76\%) of the detected KDS galaxies across both the field and cluster environments were spatially-resolved and showed clear velocity structure.
The 15 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\

The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
6/38 of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
The 32/38 morphologically isolated field galaxies are referred to as the `isolated field sample'.

@@

    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated, dispersion-dominated and merger categories.
    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

\subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
For each galaxy with spatially-resolved [O~{\sc III}]$\lambda$5007 emission we constructed a series of model datacubes with the same spatial dimensions as the observed datacube and populated each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
This central wavelength was then shifted using the velocity derived at each spaxel from the velocity field model described below.  
Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2016} the velocity field of the gas was modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:

@@

The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, rt, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
Due to the faintness of the continuum, there are several galaxies for which we could not reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter effectively doubles the signal to noise of the continuum by collapsing over twice the wavelength range. \\

@@

Following the construction of a convolved model cube and the measurement of the beam-smeared maps we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
An overview of these comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{We present here the dynamical properties for the KDS isolated field sample galaxies.
The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
Each galaxy is classified as rotation-dominated or dispersion-dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
\label{tab:kin_props}
\begin{tabular}{llllllll}

>>>>

Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$, {\it HK}-band $R\simeq2000$).
\subsubsection{Observations}\label{subsubsec:Obs}

@@

The observations were carried out during ESO observing periods P92-P96 using Guaranteed Time Observations (Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)) with excellent seeing conditions.
In GOODS-S-P1 and GOODS-S-P2 the median {\it K}-band seeing was $\simeq0.5^{\prime\prime}$ and for the SSA22-CLUSTER and SSA22-FIELD pointings the {\it K}-band seeing ranged between $\simeq0.55-0.65^{\prime\prime}$.
We observed 17-21 $z\simeq3.5$ targets in each field (see Table \ref{tab:pointings}), with these numbers less than the available 24 arms for each pointing due to the combination of three broken pickoff arms during the P92/93 observing semesters and our requirement to observe at least one control star throughout an Observing Block (OB). \\

@@

The central coordinates of each pointing, the number of target galaxies observed, N$_{obs}$, the number of galaxies with [O~{\sc III}]$\lambda$5007 detected as measured by attempting to fit the redshifted line in the integrated galaxy spectrum using the known redshift value, N$_{Det} = 62/77$ $(81\%)$, the number with spatially-resolved [O~{\sc III}]$\lambda$5007 emission, N$_{Res}$ (see \cref{subsubsection:spaxel_fitting}), the on source exposure time and the averaged seeing conditions are listed in Table \ref{tab:pointings}.

@@

The errorbars produced by {\tt GALFIT} are purely statistical and are determined from the covariance matrix used in the fitting, resulting in unrealistically small uncertainties on the derived galaxy parameters \citep{Hausler2007,Bruce2012}.
Throughout the following subsections we discuss the more reasonable adopted errors on each of the relevant morphological parameters in turn.
There is no {\em HST} coverage for 4 galaxies in our refined sample (see \cref{subsubsec:kin_sample_summary}) and in each of the following sections we also discuss the approach followed to recover the morphological parameters for these galaxies.
The interpretation of the sample as a whole is not affected by the small number of galaxies without {\em HST} imaging.

\begin{table*}
\centering
\begin{threeparttable}
\caption{Physical properties of the resolved and morphologically isolated KDS field galaxies as measured from SED fitting and from applying {\tt GALFIT} \protect\citep{Peng2010_galfit}.}
\label{tab:phys-props}
\begin{tabular}{llllllllll}

@@

ID              & RA       & Dec       & z     & K$_{AB}$     & $log(M_{\star}/M_{\odot})^{a}$ & $b/a$ & i$^{\circ}$$^{c}$ & PA$_{morph}^{\circ}$ & R$_{1/2}$(kpc)$^{d}$ \\

@@

b012141\_012208 & 03:32:23.290 & $-$27:51:57.348 & 3.471        & 24.12  & 9.84 & 0.36        & 72        & 9     & 1.57      \\
b15573          & 03:32:27.638 & $-$27:50:59.676 & 3.583        & 23.6   & 9.76  & 0.28        & 78        & 146   & 0.52      \\
bs006516        & 03:32:14.791 & $-$27:50:46.500 & 3.215        & 23.94  & 9.75 & 0.50         & 61        & 146   & 1.91      \\
bs006541        & 03:32:14.820 & $-$27:52:04.620 & 3.475       & 23.44  & 10.1  & 0.44        & 66        & 168   & 1.83      \\
bs008543        & 03:32:17.890 & $-$27:50:50.136 & 3.474        & 22.73  & 10.5 & 0.50         & 61        & 67    & 1.59      \\
bs009818        & 03:32:19.810 & $-$27:53:00.852 & 3.706        & 24.18  & 9.7  & 0.80         & 37        & 148   & 1.24      \\
bs014828        & 03:32:26.760 & $-$27:52:25.896 & 3.562        & 23.58  & 9.7  & 0.31        & 76        & 63    & 1.61      \\
bs016759        & 03:32:29.141 & $-$27:48:52.596 & 3.602       & 23.85  & 9.9   & 0.65        & 50        & 49    & 0.87      \\
lbg\_20         & 03:32:41.244 & $-$27:52:20.676 & 3.225        & 24.97  & 9.5  & 0.64        & 52        & 1     & 1.28      \\
lbg\_24         & 03:32:39.754 & $-$27:39:56.628 & 3.279       & 24.67  & 9.6   & 0.53        & 60        & 34    & 1.27      \\
lbg\_25         & 03:32:29.189 & $-$27:40:22.476 & 3.322        & 24.95  & 9.4  & 0.30         & 76        & 78    & 1.18      \\
lbg\_30         & 03:32:42.854 & $-$27:42:06.300 & 3.419        & 23.85  & 10.0  & 0.79         & 38        & 66    & 0.95      \\
lbg\_32         & 03:32:34.399 & $-$27:41:24.324 & 3.417      & 23.84  & 9.9    & 0.60         & 54        & 40    & 1.88      \\
lbg\_38         & 03:32:22.474 & $-$27:44:38.436 & 3.488       & 24.58  & 9.9   & 0.58        & 56        & 137   & 0.92      \\
lbg\_91         & 03:32:27.202 & $-$27:41:51.756 & 3.170       & 24.65  & 9.8   & 0.58        & 56        & 79    & 0.89 \\
lbg\_94         & 03:32:28.949 & $-$27:44:11.688 & 3.367       & 24.54  & 9.9   & 0.22        & 84        & 81    & 1.16      \\
lbg\_105        & 03:32:24.005 & $-$27:52:16.140 & 3.092      & 23.79  & 9.3    & 0.56        & 57        & 128   & 1.72      \\
lbg\_109        & 03:32:20.935 & $-$27:43:46.344 & 3.600       & 24.63  & 9.7   & 0.60         & 54        & 119   & 1.98      \\
lbg\_111        & 03:32:42.497 & $-$27:45:51.696 & 3.609       & 24.01  & 9.7   & 0.74        & 42        & 80    & 0.64      \\
lbg\_112         & 03:32:17.134 & $-$27:42:17.784 & 3.617        & 25.16  & 9.6 & 0.79         & 38        & 43    & 0.46      \\
lbg\_113        & 03:32:35.957 & $-$27:41:49.956 & 3.622      & 24.01  & 9.6    & 0.52        & 60        & 15    & 0.87      \\
lbg\_124         & 03:32:33.324 & $-$27:50:07.332 & 3.794        & 24.96  & 9.0  & 0.56         & 57        & 50    & 0.78      \\
$^{*}$n3\_006       & 22:17:24.859 & +00:11:17.620 & 3.069     & 22.98 & 10.5   & 0.57         & 57        & 156    & 2.52      \\
n3\_009       & 22:17:28.330 & $+$00:12:11.600 & 3.069 & -    & 8.7                       & 0.75        & 42        & 84    & 1.06      \\
n\_c3         & 22:17:32.585 & $+$00:10:57.180 & 3.096       & 24.96 & 9.8                & 0.71        & 46        & 94    & 0.56      \\
lab18         & 22:17:28.850 & $+$00:07:51.800 & 3.101           & -    & 8.2             & 0.85        & 32        & 27    & 0.46      \\
$^{*}$lab25         & 22:17:22.603 & $+$00:15:51.330 & 3.067      & -    & 8.4            & 0.57         & 57        & 87    & 2.18      \\
s\_sa22a-d3   & 22:17:32.453 & $+$00:11:32.920 & 3.069 & 23.46 & 9.7                       & 0.39        & 70        & 125   & 1.78      \\
s\_sa22b-c20  & 22:17:48.845 & $+$00:10:13.840 & 3.196     & 23.91 & 9.5                   & 0.57        & 57        & 76    & 1.59      \\
$^{*}$s\_sa22b-d5  & 22:17:35.808 & $+$00:06:10.340 & 3.175 & 23.72 & 10.2                & 0.57         & 57        & 60    & 3.30      \\
s\_sa22b-d9   & 22:17:22.303 & $+$00:08:04.130 & 3.084    & 24.25 & 10.1                  & 0.65        & 50        & 60   & 0.50       \\
$^{*}$s\_sa22b-md25 & 22:17:41.690 & $+$00:06:20.460 & 3.304     & 24.62 & 8.6             & 0.57         & 57        & 9    & 1.39

\end{tabular}
\begin{tablenotes}
      \small
      \item $^{a}$ Representative error of 0.2 dex from SED modelling used throughout this study
      \item $^{b}$ Representative error of 0.4 dex in log(SFR$_{SED}$[$M_{\odot}yr^{-1}$]) from SED modelling used throughout this study
      \item $^{c}$ Fixed 10 percent inclination error assumed (i.e. $\delta i = i / 10$, see \protect\cref{subsubsection:inclination_angle})
      \item $^{d}$ Fixed 10 percent $R_{1/2}$ error assumed, see \protect\cref{subsubsection:half-light_radii}
      \item $^{*}$ No {\em HST} coverage: $PA_{morph}$ set to $PA_{kin}$ value; $b/a$ and $R_{1/2}$ estimated as explained throughout the text.
    \end{tablenotes}
  \end{threeparttable}
  \end{table*}

@@

As mentioned in \cref{subsubsec:galfitting}, the error reported by {\tt GALFIT} on the model $b/a$ value is unrealistically small.
Guided by the results of the Monte Carlo approach described in \cite{Epinat2012} we adopted a conservative nominal inclination angle uncertainty of 10$\%$, i.e. $\delta i = i / 10$.
For the galaxies without {\em HST} coverage the inclination angle was set to the KDS sample median of 57.0$^{\circ}$ and we used the standard deviation of the KDS inclinations, 13.2$^{\circ}$, for the inclination uncertainty.
This adds an additional factor of $\simeq1.3$ to the uncertainty in the derived velocities for these galaxies.

@@

If a spaxel did not meet the criteria we follow the procedure described in \cite{Stott2016} and binned with neighbouring spaxels to create a box of area $0.3\times0.3^{\prime\prime}$.
This was carried out by median stacking the extraction region spectra in each of the neighbouring spaxels.
The criteria were then re-examined, and if satisfied, the Monte-Carlo procedure was carried out. 
If the binned spaxels fail the criteria, one final iteration was carried out to bin to a box of area $0.5\times0.5^{\prime\prime}$, roughly equivalent to the size of the seeing disk (see Table \ref{tab:pointings}).
If after the widest binning the criteria weren't satisfied, no value was assigned to that spaxel in the extracted maps. \\

The process was automated and applied to each of the 62/77 KDS galaxies with an [O~{\sc III}]$\lambda$5007 detection.
Following the fitting procedure the galaxies were clasified as spatially-resolved in [O~{\sc III}]$\lambda$5007 emission or not if the spatial extent of the accepted spaxels in the [O~{\sc III}]$\lambda$5007 flux map was equivalent to or greater than the seeing disk.
For each pointing, the number of resolved galaxies, N[O~{\sc III}]$_{Res}$, was added to Table \ref{tab:pointings}.
We find that 47/77 (76\%) of the detected KDS galaxies across both the field (38) and cluster (9) environments were spatially-resolved and showed clear velocity structure.
The 15/77 galaxies which were not spatially-resolved were dropped at this stage due to the uncertainties associated with deriving kinematic properties and classifications from a single resolution element.
The physical properties of all spatially-resolved galaxies in both GOODS-S and SSA22 are listed in Table \ref{tab:phys-props}. \\

The morphological information of \cref{subsec:morphological_measurements} was combined with this spatially-resolved condition to define two galaxy subsamples.
6/38 (16\%) of the resolved galaxies across the 3 field environment pointings and almost all of the cluster environment galaxies in SSA22-P1 have multiple photometric components, which complicate the interpretation of the observed dynamics for these targets.
We dropped the cluster environment pointing from the full dynamical analysis, although we show examples of the {\em HST} imaging, flux, dispersion and velocity maps of the cluster target galaxies in \cref{fig:merger_galaxies}.
The remaining 6/38 merging candidates in the field environment are referred to as the `merger field sample' throughout the remainder of the paper.
The 32/38 morphologically isolated field galaxies which are spatially resolved are referred to as the `isolated field sample' throughout the remainder of the paper.

@@

    \caption{We plot the kinematic grids for one rotation-dominated galaxy (top grid), one dispersion-dominated galaxy (middle grid) and one merger candidate (bottom grid) (see \protect\cref{subsec:morpho-kin-class}) from the KDS.
    In Appendix \protect\ref{app:kinematics_plots} we include these plots for each of the spatially-resolved galaxies in the KDS, divided into rotation-dominated (13/38), dispersion-dominated (19/38) and merger categories (6/38).
    For each galaxy we plot on the top row the {\em HST} image, {\tt GALFIT} model and {\tt GALFIT} residuals, along with the observed [O~{\sc III}]$\lambda$5007 intensity map and velocity dispersion map. 
    On the bottom row we plot the observed velocity map, the beam-smeared model velocity and data-model velocity residuals with colour bar limits tuned to the velocity model.
    The solid black line and dashed orange line plotted in various panels show $PA_{kin}$ and $PA_{morph}$ respectively.
    Also on the bottom row, we plot extractions along $PA_{kin}$ for both the velocity and velocity dispersion.
    The grey points with errorbars on the velocity extraction plot are from the observed velocity map, the blue line and blue shaded regions represent the beam-smeared model fit to the data and errors respectively, whereas the red line and shaded regions are the intrinsic model from which $V_{C}$ is extracted.
    The purple symbols represent the extraction along $PA_{kin}$ from the residual map and the red and blue dashed lines denote the intrinsic and convolved $2R_{1/2}$ values respectively, with $V_{C}$ extracted at the intrinsic value and $V_{BS}$ extracted at the convolved value of the intrinsic and observed profiles respectively.
    The intrinsic models flatten at small radii, and so small changes in $R_{1/2}$ have negligible impact on the final, extracted $V_{C}$ values.
    The blue points on the velocity dispersion extraction plot show the values extracted from the observed dispersion map and the red are from the beam-smearing corrected map as per Equation \protect\ref{eq:dispersion_comp}.
    Also on the 1D dispersion plot we include with the blue and red dot-dash horizontal lines median values of the observed and intrinsic (i.e. $\sigma_{int}$) dispersion maps respectively.
    The merger candidate in the bottom grid requires several {\tt GALFIT} components to describe the data, mimics rotation from a purely kinematic perspective and we plot the 1D extractions without beam-smearing corrections, which are not warranted for multiple component objects.}
    \label{fig:main_body_kinematic_grids}

@@

\subsubsection{Constructing model datacubes}\label{subsubec:model_cube}
For each galaxy with spatially-resolved [O~{\sc III}]$\lambda$5007 emission we constructed a series of model datacubes with the same spatial dimensions as the observed datacube and populated each spaxel with an [O~{\sc III}]$\lambda$5007 emission line that has central wavelength determined using $z_{sys}$.
This central wavelength was then shifted using the velocity derived at each spaxel from the velocity field model described below.  
Following the procedure adopted by numerous authors \citep[e.g.][]{Epinat2010,Epinat2012,Swinbank2012,Stott2016,Mason2017} the velocity field of the gas was modelled as a thin disk with the discrete velocity points along $PA_{kin}$ determined by Equation \ref{eq:arctangent}, which has been found to reproduce the rotation curves of galaxies in the local universe \citep[e.g.][]{Courteau1997}:

@@

The velocity decreases with a factor of cos($\phi$) from the kinematic position axis, where $\phi$ is the angle measured clockwise from the axis, which points to the direction of the positive side of the velocity field.
The 6 free parameters of the model; $(xcen, ycen), i, PA_{kin}, r_{t}, v_{asym}$, were first reduced to 5 by using the inclination from the {\em HST} axis ratio.
We also fixed the (xcen,ycen) parameters to the location of the stellar continuum peak within the collapsed cubes, a proxy for the centre of the gravitational potential well, to leave only 3 free parameters to vary in the MCMC sampling.
Due to the faintness of the continuum, there are several galaxies for which we could not reliably estimate the rotation centre using this method and instead set (xcen,ycen) to coincide with the peak [O~{\sc III}]$\lambda$5007 flux location (approach described in \citealt{Harrison2017}).
Using the continuum to fix the rotation centre was generally more successful for the SSA22 galaxies, since the use of the {\it HK} filter increases the signal to noise of the continuum by collapsing over twice the wavelength range. \\

@@

Following the construction of a convolved model cube and the measurement of the beam-smeared maps we extract beam-smearing corrected values for $V_{C}$ and $\sigma_{int}$, as described throughout the following subsections.
There have been several different methods used to extract $V_{C}$ and $\sigma_{int}$ in previous surveys at different redshifts.
We select a set of comparison samples with similar galaxy selection criteria and kinematic parameter extraction methods to those described above in order to make comparisons with the KDS across different redshift slices (see \cref{sec:results}).
We have re-evaluated the means and medians of the kinematic properties in these samples in order to make fair and reliable comparisons.
An overview of the comparison samples is provided in Appendix \ref{app:comparison_samples}, which also describes the approach used to compute average parameter values.

@@

\begin{table*}
\centering
\begin{threeparttable}
\caption{The dynamical properties for the KDS isolated field sample galaxies.
The observed properties are measured directly from the extracted two-dimensional maps, whereas $V_{C}$ and $\sigma_{int}$ have been corrected for the effects of beam-smearing as described throughout the text.
Each galaxy is classified as rotation-dominated or dispersion-dominated if the ratio $V_{C}/\sigma_{int}$ is greater than or less than 1 respectively, as highlighted in the `Class' column.}
\label{tab:kin_props}
\begin{tabular}{llllllll}
